Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-14 article.tex
Modification biblio style et ajout d'un mot au glossaire

@@

A Delaunay triangulation of a set of points in the plane subdivides their convex hull into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.

@@

\bibliographystyle{alpha}
\bibliography{./biblio.bib}

>>>>

\newglossaryentry{convHull}
{
    name=convex hull,
    description={The smallest convex set containing a given set}
}

@@

A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{del_tri}.

@@

\bibliographystyle{IEEEtran}
\bibliography{./biblio.bib}
